Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-19 manuscript.Rmd
overall metric table

>>>>

```{r metricstable}

metrics_long %>% group_by(Model, metric) %>% 
  get_summary_stats(value) %>% 
  select(-(variable:max), -(q1:mad), -se, -ci) %>% 
  pivot_wider(names_from = Model, values_from = c("median", "mean", "sd")) %>% 
  filter(metric != "Neg Pred Value", metric != "Specificity") %>% 
  relocate(mean_Group, .after = median_Group) %>% 
  relocate(sd_Group, .after = mean_Group) %>% 
  mutate(across(-metric, ~ apa_num(.x, digits = 3)),
         metric = factor(metric, levels = metric_labels)) %>% 
  arrange(metric) %>% 
  apa_table(., col.names = c("Metric", "Median", "Mean", "SD", "Median", "Mean", "SD"),    col_spanners = list("Group" = c(2, 4), "Individual" = c(5, 7)),
          caption = "Summary statistics for model performance metrics shown separately for group and individual models.")
```

### 2023-02-19 manuscript.tex
overall metric table

@@

\caption{\label{tab:agetable}Summary of age differences in full-day body position for younger (4- to 7-month) and older (11- to 14-month) infants. Values shown are the mean percent of time for each body position averaged across infants in each group.  extit\{SD\} is shown in parentheses. Estimates are shown separately for group and individual models.}

>>>>

\caption{\label{tab:metricstable}Summary statistics for model performance metrics shown separately for group and individual models.}

\begin{tabular}{lllllll}
\toprule
 & \multicolumn{3}{c}{Group} & \multicolumn{3}{c}{Individual} \\
\cmidrule(r){2-4} \cmidrule(r){5-7}
Metric & Median & Mean & SD & Median & Mean & SD\\
\midrule
Overall Accuracy & 0.908 & 0.848 & 0.143 & 0.936 & 0.919 & 0.071\\
Balanced Accuracy & 0.909 & 0.897 & 0.074 & 0.916 & 0.907 & 0.072\\
F1 & 0.813 & 0.827 & 0.101 & 0.873 & 0.870 & 0.089\\
Sensitivity & 0.840 & 0.836 & 0.123 & 0.848 & 0.840 & 0.121\\
Pos Pred Value & 0.822 & 0.815 & 0.125 & 0.915 & 0.899 & 0.108\\
Kappa & 0.769 & 0.757 & 0.160 & 0.846 & 0.820 & 0.141\\
\bottomrule
\end{tabular}

@@

\caption{\label{tab:agetable}Summary of age differences in full-day body position for younger (4- to 7-month) and older (11- to 14-month) infants. Values shown are the mean percent of time for each body position averaged across infants in each group. Standard deviations are shown in parentheses. Descriptive statistics are shown separately for group and individual models.}
